Coherent optical creation of a single molecule

### 2020-12-07 paper.tex
Update on Overleaf.

\begin{abstract}
  We report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
  The molecules have a binding energy of $770.2~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$.
  This technique does not rely on Feshbach resonances or narrow excited-state lines
  and may allow a wide range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques
that have been developed for atoms.
Associating atoms into deeply bound molecules is challenging
because of the small wavefunction overlap between the free-atom and molecular states
and the release of a large amount of binding energy.
A widely used method of overcoming these challenges is to associate atom pairs
into weakly bound molecules first,
and then transfer the molecules from this single internal state
to a desired rovibrational and electronic state,
releasing the binding energy by stimulated emission~\cite{Danzl2008, Ni2008, Lang2008,
  Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, molecular association has generally been achieved by magnetoassociation
through a magnetic Feshbach scattering resonance.
Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
and $^{87}$Rb$^{85}$Rb,
where there are molecular states bound by $1-2~\mathrm{MHz}$~\cite{He331}.
With these requirements, molecules involving non-magnetic atoms
or atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited-state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
by two-photon optical Raman transfer via an electronic excited state,
as shown in Fig.~\ref{f-theory}a.
The scheme does not rely on a Feshbach resonance,
molecular states bound by a few~MHz, or a narrow excited state.
The resulting single molecule is in a well-defined internal quantum state
and predominantly in its motional ground state.
A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
serves as the intermediate state in the Raman scheme,
and is chosen to minimize photon scattering during Raman Rabi oscillations.
To reduce photon scattering and sensitivity to laser intensity noise further,
we choose the initial and final states to balance the two Rabi frequencies as much as possible.
This approach applies to a variety of molecules that can be created atom-by-atom with full quantum state control.

@@

The optical Raman transfer is illustrated
by the idealized three-level system shown in Fig.~\ref{f-theory}a,
where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_a$ and $\Omega_m$ with one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
The transfer Raman Rabi Rate is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
% , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced ($\Omega_a/\Omega_m \ll 1$) %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and scattering losses are dominated by the final state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning $ \Delta $ of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi rate at fixed total power, resulting in a factor of 2 for scattering two beams.}.
In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state. At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift ($\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
  to account for the Stark shift caused by both beams.}. Notably, both figures of merit improve with a larger ratio $\Omega_a/\Omega_m$. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
%However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
  \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
    (a) Raman difference frequency scans for various durations showing the resonance as a frequency offset from $770.2$~MHz, near the calculated value of $763$~MHz.
    (b) Raman pulse-length scan on resonance.
    A decaying Rabi oscillation shows the coherence of
    the Raman transfer process.
    A model is fitted to (a) and (b) to determine
    the Raman Rabi frequency and loss rates.
    \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
    The X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
    that confines the atoms and molecule.
    A perpendicular $B_0=8.83(2)~\mathrm{G}$ magnetic field 
    defines the quantization axis and the atoms experience predominantly $\pi$-polarized light.
    \label{f-raman}}
\end{figure}

@@

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
by performing a Cs spin flip while taking into account
the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
This is the initial atomic state for Raman transfer.
The spin flip selectively transfers atoms in the relative motional ground state,
removing any background from atoms in excited motional states
\footnote{This interaction shift is larger than the differential axial trapping frequency
  between Na and Cs atoms, which decouples the relative and center of mass motional state
  and improves the robustness of our preparation of the relative motional ground state.}.
For the experiment reported here,
$31\mathrm{\%}$ of initial two-atom population is transferred.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To transfer the atom pair into the target weakly bound molecular state,
we modulate the tweezer beam with a second frequency near $770$~MHz, as shown in Fig.~\ref{f-beampath}.
The dual use of the tweezer beam for confinement and Raman transfer not only minimizes photon scattering,
but also allows a tight focus to minimize the transfer duration. A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from $v' = 0 $ ($<50$~MHz natural linewidth) reduces resonant scattering~\cite{Liu2019}.
%Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
%clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
%As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
%The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here? or the possible causes?}). While we have not fully characterized the sources
%of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
% After the total tweezer power is set to the desired value,
% we smoothly ramp down the power of one frequency in the tweezer
% while simultaneously ramping up the power of the other frequency
% so that the total tweezer power remains unchanged.
% Both frequencies are kept on for a specified duration before the process is reversed
% and the tweezer returns to a single frequency.~\TR{???}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime with about $X.XX~\mathrm{mW}$ optical power.
    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    Inset: pulse sequence for the lifetime measurement.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $X.XX~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as
    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
$69~\mathrm{\%}$ of atoms initially in the relative motional ground state are transferred into the molecular state after a $\pi$-pulse. Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer power and detuning.
    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are the power ($P$) dependent background and $v'=0$ contributions
    to the light shift and
    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
    the $v'=0$ resonance frequency $f_0$.
    $a_P$ is fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
    $P^{0.79}$ scaling of $\Omega_a$. [[TR: There should be a gap between (c) top and bottom.]
    \label{f-det}}
\end{figure*}

@@

The measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials). From the full calculation of the expected scattering rate including all excited states
%Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig. 3b~\TR{long sentence}.  Below, we further investigate the loss of coherence.

\todo{change scattering to decoherence? since the fluctuation of light shift
  does not lead to scattering but only decherence.}
% These results suggest that the decoherence or loss we observe during the Raman transition
% comes from either a higher background scattering rate of an unknown source
% or a different intrinsic or technical source for which we have not accounted for.
Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
The lifetime is measured directly by preparing the molecule with a $\pi$-pulse,
followed after a variable delay by a second dissociating $\pi$-pulse.
The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$,
consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.  Atom loss is shown to be small in Fig.~\ref{f-lifetime} by measuring the one- and
two-body lifetimes of the atoms directly without the second Raman frequency.  In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances made the positive region unusable.  Separately we observe a decrease in coherence by a factor of 2 without laser spectrum filters,
suggesting that spectral impurity of the laser can be a significant source of loss.

Other potential decoherence sources include
fluctuations of the tweezer intensity and magnetic field.
Based on the Rabi frequency ratio in Table~\ref{tab:f-det:fit}
the requirement on the tweezer intensity stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$ power. We stabilize the power to $0.1\mathrm{\%}$, indicating that in the absence of beam-waist fluctuations, light shift is not a major source of decoherence.
Similarly, the measured Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
does not cause significant decoherence for the measured magnetic field
fluctuation of $1.5~\mathrm{mG}$.

@@

Our technique can be applied to form a diverse set of molecular species,
because it does not rely on a magnetic Feshbach resonance, states bound by only a few MHz,
or a narrow excited state. The formation of weakly bound molecules is a key step
in forming rovibrational ground state molecules. By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved. These molecules comprise a flexible platform for quantum simulation and quantum computing applications. \textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
% Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
% defect-free arrays of highly controlled molecules comprise a promising
% and flexible platform for quantum simulation and quantum computing applications.

@@

\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates molecular loss, not atomic loss or frequency fluctuation.}

>>>>

\begin{abstract}
  We report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition.
  The Raman technique uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
  The molecules have a binding energy of $770.2~\mathrm{MHz}$ at $8.83(2)~\mathrm{G}$.
  This technique does not rely on Feshbach resonances or narrow excited-state lines
  and may allow a wide range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques
that have been developed for atoms.
Associating atoms into deeply bound molecules is challenging
because of the small wavefunction overlap between the free-atom and molecular states
and the release of large binding energy.
A widely used method of overcoming these challenges is to associate atom pairs
into weakly bound molecules first,
and then transfer the molecules from this single internal state
to a desired rovibrational and electronic state,
releasing the binding energy by stimulated emission~\cite{Danzl2008, Ni2008, Lang2008,
  Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, molecular association has generally been achieved by magnetoassociation
through a magnetic Feshbach scattering resonance.
Exceptions include Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
With these requirements, molecules involving non-magnetic atoms
or atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited-state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
by two-photon optical Raman transfer via an electronic excited state,
as shown in Fig.~\ref{f-theory}a.
The technique does not rely on a Feshbach resonance,
molecular states bound by a only few~MHz, or a narrow excited state.
The resulting single molecule is in a well-defined internal quantum state
and predominantly in its motional ground state.
A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
serves as the intermediate state in the Raman technique,
and is chosen to minimize photon scattering during Raman Rabi oscillations.
To reduce photon scattering and sensitivity to laser intensity noise further,
we choose the initial and final states to balance the two Rabi frequencies as much as possible.
This approach applies to a variety of molecules that can be created atom-by-atom with full quantum state control.

@@

The optical Raman transfer is illustrated
by the idealized three-level system shown in Fig.~\ref{f-theory}a,
where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies $\Omega_a$ and $\Omega_m$ with one-photon detuning $ \Delta $, and all Rabi frequencies are population oscillation frequencies.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
The transfer Raman Rabi frequency is given by $\Omega_a\Omega_m / (2\Delta)$~\cite{Wineland2003}.
% , is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced ($\Omega_a/\Omega_m \ll 1$) %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and scattering losses are dominated by the final state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning $ \Delta $ of $80$ to $200$~GHz, causing the target molecular state to scatter both beams nearly equally with a total rate $ \Gamma_e \Omega_m^2 / (2\Delta^2)$, where $ \Gamma_e $ is the excited-state linewidth~\footnote{The two beams have equal power to maximize the Raman Rabi rate at fixed total power, resulting in a factor of 2 for scattering two beams.}.
In this idealized treatment, the ratio between the Raman Rabi frequency and the scattering rate is $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, which limits the transfer efficiency into the molecular state. At the same time, the intensity-stability requirement is determined by the ratio of Raman Rabi frequency to light shift ($\Omega_a/\Omega_m$)~\footnote{There is an additional factor of 2, with both beams at equal power,
  to account for the Stark shift caused by both beams.}. Notably, both figures of merit improve with a larger ratio $\Omega_a/\Omega_m$. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
% However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.

@@

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ with a large scattering length
by performing a Cs spin flip while taking into account
the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
This is the initial atomic state for Raman transfer.
The spin flip selectively transfers atoms in the relative motional ground state,
removing any background from atoms in excited states of relative motion
\footnote{This interaction shift is larger than the differential axial trapping frequency
  between Na and Cs atoms, which decouples the relative and center of mass motional state
  and improves the robustness of our preparation of the relative motional ground state.}.
For the experiment reported here,
$31\mathrm{\%}$ of initial two-atom population is transferred. Of this population, over $60\%$ is in the ground state of center of mass motion, inferred from Raman sideband thermometry~\cite{Zhang2020,He331}. %center-of-mass motional ground state.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
  \caption{Coherent transfer of atoms to molecules.  The molecular state is dark to the imaging step and corresponds to zero signal.
    (a) Raman difference frequency scans for various durations showing the resonance as a frequency offset from $770.2$~MHz, near the calculated value of $763$~MHz.
    (b) Raman pulse-length scan on resonance.
    A decaying Rabi oscillation shows the coherence of
    the Raman transfer process.
    A model is fitted to (a) and (b) to determine
    the Raman Rabi frequency and loss rates.
    \emph{Inset:} Geometry and polarization of trap and Raman beam relative to the magnetic field.
    The X.yy~mW beam is focused to a waist of $0.9~\mathrm{\mu m}$
    that confines the atoms and molecule.
    A perpendicular $B_0=8.83(2)~\mathrm{G}$ magnetic field
    defines the quantization axis and the atoms experience predominantly $\pi$-polarized light.
    \label{f-raman}}
\end{figure}
%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To transfer the atom pair into the target weakly bound molecular state,
we modulate the tweezer beam with a second frequency near $770$~MHz, as shown in Fig.~\ref{f-beampath}.
The dual use of the tweezer beam for confinement and Raman transfer not only minimizes photon scattering,
but also allows a tight focus to minimize the transfer duration. A tweezer frequency far detuned (by $-151~\mathrm{GHz}$) from $v' = 0 $ ($<50$~MHz natural linewidth) reduces resonant scattering~\cite{Liu2019}.
% Furthermore, two filters, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
% clean the laser spectrum and prevent broadband noise from causing unwanted excitation.
% As shown in Fig.~\ref{f-beampath}, one filter immediately follows the laser, while the second filter precedes the microscope objective for final cleanup of the laser spectrum.
% The filters reduce photon scattering rate by a factor of $2$ (\textcolor{red}{KW: Since we mention this again later when we explore the causes of our lower than expected transfer efficiency, do we need to mention this reduction here? or the possible causes?}). While we have not fully characterized the sources
% of broadband noise, possibilities include amplified spontaneous emission (ASE) from the laser and fiber nonlinearities.
% After the total tweezer power is set to the desired value,
% we smoothly ramp down the power of one frequency in the tweezer
% while simultaneously ramping up the power of the other frequency
% so that the total tweezer power remains unchanged.
% Both frequencies are kept on for a specified duration before the process is reversed
% and the tweezer returns to a single frequency.~\TR{???}

@@

\begin{figure*}[t!]
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer power and detuning.
    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are the power ($P$) dependent background and $v'=0$ contributions
    to the light shift and
    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
    the $v'=0$ resonance frequency $f_0$.
    $a_P$ is fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
    $P^{0.79}$ scaling of $\Omega_a$. 
    \label{f-det}}
\end{figure*}

Figure~\ref{f-raman} shows a Fourier-limited resonance together with Rabi oscillations between the atomic and molecular states.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
A decaying Rabi oscillation with frequency $2\pi\times3.28(4)~\mathrm{kHz}$ fitted to the data suggests that
$69~\mathrm{\%}$ of atoms are transferred into the molecular state after a $\pi$-pulse with the majority of molecules in the ground state of motion. 
%Over $60\%$ of the molecules are in the motional ground state (both relative and center of mass), inferred from independent Raman sideband thermometry measurements of the atoms.

@@

The measured single-photon Rabi frequencies of Table~I are in broad agreement with calculations (see Supplementary Materials). 
The full calculation of the expected scattering rate of the molecular and atomic state including all excited states does not explain the decoherence in Fig.~\ref{f-raman}b. 
% Known single-photon scattering rates of Na and Cs atoms together with an independent measurement (via photoassociation spectroscopy) of the $v'=0$ excited state natural linewidth of no more than $50~\mathrm{MHz}$ indicate that single-photon scattering from the molecular or atomic state do not explain the decoherence in Fig. 3b~\TR{long sentence}.  Below, we further investigate the loss of coherence.
%\todo{change scattering to decoherence? since the fluctuation of light shift
%  does not lead to scattering but only decherence.}
% These results suggest that the decoherence or loss we observe during the Raman transition
% comes from either a higher background scattering rate of an unknown source
% or a different intrinsic or technical source for which we have not accounted for.
From experimental measurements, the Raman transfer efficiency is limited by the molecular lifetime, together with a reduction in the Raman Rabi frequency due to destructive interference with intermediate states beyond v'=0 (see Table~~\ref{tab:f-det:fit}).
The lifetime is measured directly by preparing the molecule with a $\pi$-pulse,
followed after a variable delay by a second dissociating $\pi$-pulse.
The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$,
consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b.
Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.  Atom loss is shown to be small in Fig.~\ref{f-lifetime} by measuring the one- and
two-body lifetimes of the atoms directly without the second Raman frequency.  In principle, destructive interference that reduces the Raman Rabi rate for negative detunings $\Delta$ changes to constructive interference for positive detunings, but additional molecular resonances made the positive region unusable.  Separately we observe a decrease in coherence by a factor of 2 without laser spectrum filters,
suggesting that spectral impurity of the laser can be a significant source of loss.

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime with about $X.XX~\mathrm{mW}$ optical power.
    Molecule survival is detected by dissociating back to atoms via a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    Inset: pulse sequence for the lifetime measurement.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $X.XX~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as
    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}
Other potential decoherence sources include
fluctuations of the tweezer intensity and magnetic field.
Based on the Rabi frequency ratio in Table~\ref{tab:f-det:fit}
the requirement on the tweezer intensity stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$ power. We stabilize the power to $0.1\mathrm{\%}$, indicating that in the absence of beam-waist fluctuations, light shift is not a major source of decoherence.
Similarly, the measured Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
does not cause significant decoherence for the measured magnetic field
fluctuation of $1.5~\mathrm{mG}$.

@@

Our technique can be applied to form a diverse set of molecular species,
because it does not rely on a magnetic Feshbach resonance, states bound by only a few MHz,
or a narrow excited state. The formation of weakly bound molecules is a key step
in forming rovibrational ground state molecules. By scaling up to many optical tweezers~\cite{Endres2016, Barredo2018,  PhysRevLett.122.203601}, large arrays with arbitrary geometry of highly controlled molecules can be achieved. These molecules comprise a flexible platform for quantum simulation and quantum computing applications. %\textcolor{blue}{(End with a sentence on molecules for future quantum applications?)}
% Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
% defect-free arrays of highly controlled molecules comprise a promising
% and flexible platform for quantum simulation and quantum computing applications.

@@

\TR{Mention somewhere that the shape of Fig. 3b Rabi flopping indicates loss, not frequency fluctuation.}
